Pricing Games in Heterogeneous Parallel Networks

### 2025-02-07 thesis/slides.tex
Thesis: Pres: Improvements over all sections
History graph, Preliminaries and Pricing Games cleanup and restructuring, Sensitivity Split partial cleanup and some extra Future Work

\mode<presentation>
{
	\usetheme[progressbar=foot,numbering=fraction,background=light,block=fill]{metropolis}
	\usecolortheme{default}
	\usefonttheme{default}
	\setbeamertemplate{navigation symbols}{}
	\setbeamertemplate{caption}[numbered]
	\setbeamertemplate{frame footer}{Thomas Pappas | ALMA }
}

@@

\title[]{Pricing Games in Heterogeneous Parallel Networks}
\author[Thomas Pappas]{Thomas Pappas}
\institute[ALMA]{
	\begin{columns}
		\column{0.4\textwidth}
		\begin{figure}
			\centering
			\includegraphics[scale=0.1]{alma.png}
		\end{figure}
		\column{0.5\textwidth}
		ALMA \\
		\tiny{INTER-INSTITUTIONAL GRADUATE PROGRAM \\
			"ALGORITHMS, LOGIC AND DISCRETE MATHEMATICS"}
	\end{columns}
}
\date{\today}

@@

\section{Introduction}

\begin{frame}{History}
	\begin{itemize}
		\item Selfish routing \footcite{pigou1920economics}
		\item Congestion games \footcite{Rosenthal1973ACO}
		\item Wardrop equilibrium \footcite{wardrop_theoretical_1952}
		\item Pricing competition \footcite{10.1287/moor.1060.0231}
		\begin{itemize}
			\item Homogeneous case with toll caps \footcite{Harks_2019}
		\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}{Our model}
	\begin{center}
		Heterogeneous Non-atomic $n$-link Parallel Network\\
		Toll Congestion Pricing Game
	\end{center}
\end{frame}
\begin{frame}{Our model}
	\begin{center}
		\textbf{Heterogeneous} Non-atomic $n$-link Parallel Network\\
		Toll Congestion \textbf{Pricing} Game
	\end{center}
\end{frame}

\begin{frame}{Our model}
	\;
	\begin{block}{$2$-level game}
		\begin{enumerate}
			\item Shelfish routing game, flow on minimum cost paths
			\item Profit maximisation game for link operators
		\end{enumerate}
	\end{block}
\end{frame}

\begin{frame}{Preliminaries}
	\;
	\begin{block}{Non-atomic $n$-link Parallel Network Game}
		A \textbf{Parallel Network} is a directed graph $G = (\{s, t\}, N)$, where $N = \{1, \dots, n\}$ a set of $n$ parallel $s-t$ links.

@@

\begin{frame}{Preliminaries}
	\;
	\begin{block}{Non-atomic $n$-link Parallel Network Game}
		Flow $f: [0, 1] \rightarrow N$ is a Lebesque measurable function assigning players to links.

@@

\begin{frame}{Homogeneous players}
	Links can be tolled by assigning tolls $t \in \R_+^N$.

	Player $p$ experiences on link $i$ total cost $c_i(p) = \ell_i(x_i) + t_i$.
	\begin{definition}
		For a given set of tolls $t$, a flow $x$ is a \textit{Wardrop equilibrium for $t$} if $\forall i, j \in N$ with $x_i > 0$ it holds that
		\begin{equation*}
			\ell_i(x_i) + t_i \leq \ell_j(x_j) + t_j
		\end{equation*}
	\end{definition}
	Links with $x_i > 0$ have $\ell_i(x_i) + t_i = K$ for some $K > 0$.

	Wardrop equilibrium always exits and is unique\footcite{??}, denote it by $x(t)$.
\end{frame}

\begin{frame}{Homogeneous players}
	\begin{lemma}[variational inequality\footcite{dafermos1973toll}]
		A flow $x$ is a Wardrop equilibrium for $t$ if and only if for all feasible flows $x^\prime$,
		\[\sum_{i \in N} (\ell_i(x_i) + t_i) \cdot (x_i - x_i^\prime) \leq 0\]
	\end{lemma}
	Equilibrium is indifferent to uniform variations of tolls ($t^\prime = t + c$) or (affine) latencies.
\end{frame}

\begin{frame}{Heterogeneous players}
	Players value time-money differently, so add weight $\alpha$ to money.
	\begin{block}{Distribution function $\alpha: [0, 1] \rightarrow [0, +\infty]$}
		\begin{itemize}
			\item players are ordered w.r.t. sensitivity
			\item $\alpha$ is non-decreasing
		\end{itemize}
	\end{block}
	Player $p$ experiences on link $i$ total cost $c_i(p) = \ell_i(x_i) + \alpha(p) \cdot t_i$.
	\begin{definition}
		For a given set of tolls $t$, a flow $x$ is a \textit{Nash equilibrium for $t$} if for all players $p \in [0, 1]$ and $\forall i \in N$ it holds that
		\begin{equation*}
			c_{f(p)}(p) \leq c_i(p)
		\end{equation*}
	\end{definition}
\end{frame}

\begin{frame}{Heterogeneous players}
	\begin{example}
		Let $([2], \ell, \alpha)$ with $\ell_1(x) = 2x, \ell_2(x) = x + 1$ and $\alpha(p) = p + 1$.
	\end{example}
	\begin{center}
		\begin{tikzpicture}[scale=1.4, every node/.style={font=\small}]
			% Nodes
			\node[circle, draw, fill=blue!20, minimum size=0.8cm] (s) at (0,0) {$s$};
			\node[circle, draw, fill=blue!20, minimum size=0.8cm] (t) at (4,0) {$t$};

			% Links
			\draw[->, thick] (s) to[bend left=35] node[midway, above] {$2x$} (t);
			\draw[->, thick] (s) to[bend right=35] node[midway, below] {$x + 1$} (t);

			% Description
			%\node[align=center] at (2, -2) {Network of Example};
		\end{tikzpicture}
	\end{center}
	$x(0) = \left(\frac23, \frac13\right), \; x(3, 2) = \left(\frac14, \frac34\right)$
\end{frame}

\begin{frame}{Heterogeneous players}
	Nash equilibrium for $t$ always exists\footcite{1973JSP.....7..295S} and is unique\footcite{MILCHTAICH1996111}, again denote it by $x(t)$.
\end{frame}

\begin{frame}{Pricing competition (2\textsuperscript{nd} level)}
	Links are owned by agents who compete for profit.
	\begin{block}{Profit}
		For given set of tolls $t \in \R_+^N$, link operator $i$ gains profit
		\[\Pi_i(t) = x_i(t) \cdot t_i\]
	\end{block}

	\begin{block}{Best response}
		For fixed tolls assignments from remaining link operators $t_{-i} = t \setminus \{t_i\}$, link operator $i$ will try and maximise their profit
		\[B_i(t_{-i}) = \argmax_{t_i \ge 0} \Pi(t_i, t_{-i})\]
	\end{block}
\end{frame}

\begin{frame}{Pricing competition (2\textsuperscript{nd} level)}
	\begin{block}{Nash Equilibrium}
		A given set of tolls $t$ is a \textit{Nash Equilibrium for the pricing game} if $\forall i \in N$ and $\forall t_i^\prime \in \R_+$
		\[\Pi_i(t_i, t_{-i}) \geq \Pi_i(t_i^\prime, t_{-i})\]
	\end{block}
	\begin{block}{Nash Equilibrium}
		A given set of tolls $t$ is a \textit{Nash Equilibrium for the pricing game} if
		$\forall i \in N$ we have $|B_i(t_{-i})| = 1$ and
		\[t = (B_i(t_{-i}))_{i \in N}\]
	\end{block}
\end{frame}

\begin{frame}{Game equivalence}
	\begin{definition}[Game equivalence]
		Let $\Gm_1, \Gm_2$ be two $n$-link Network Congestion Games.
		$\Gm_1$ and $\Gm_2$ are called \textbf{equivalent} if and only if for all tolls $t \in \R_+$ it holds that $x^{(1)}(t) = x^{(2)}(t)$, with $x^{(1)}(t), x^{(2)}(t)$ being the Nash Equilibria for $t$ in $\Gm_1, \Gm_2$ respectively.
	\end{definition}
	The two pricing competition games played on two equivalent network congestion games are identical.
\end{frame}

\section{Heterogeneous players}

\begin{frame}{Heterogeneous players}
	\begin{lemma}
		For $\Gm = (N, \ell, \alpha)$ with tolls $t$ and flow $x(t)$ the Nash equilibrium for $t$, it holds for all $i, j \in N$ with $x_i(t), x_j(t) > 0$ that
		\begin{enumerate}[(i)]
			\item $\ell_i(x_i(t)) < \ell_j(x_j(t))$ iff $t_i > t_j$
			\item $\ell_i(x_i(t)) = \ell_j(x_j(t))$ iff $t_i = t_j$
			\item $\ell_i(x_i(t)) > \ell_j(x_j(t))$ iff $t_i < t_j$
		\end{enumerate}
	\end{lemma}
	\begin{proof}
		Assume $\ell_i(x_i(t)) < \ell_j(x_j(t))$ and $t_i < t_j$ for some $i, j \in N$.
		Then for \textbf{all} players $c_i(p) < c_j(p)$ so $x_j(t) > 0$ is a contradiction.
	\end{proof}
\end{frame}

\begin{frame}{Heterogeneous players}
	Latencies are viewed the same for all players.

@@

@@

	In example ?? the users are organised around the one for which $c_1(p) = c_2(p)$.

@@

\begin{frame}{Sensitivity split}
	\begin{definition}
		\label{definition:alpha_flow_sets}
		Let $(N, \ell, \alpha)$ a heterogeneous parallel game, tolls $t$ and $x(t)$ the Nash equilibrium for $t$.
		We define as $A_i(t)$ the set of all possible $\alpha(p)$ values of players $p$ using link $i$ in the Nash equilibrium for $t$.
		We define a set function $A_i: \R_+^{|N|} \rightarrow \mathcal{P}(\R_+)$, where $\mathcal{P}(\R_+)$ is the powerset of $\R_+$, such that
		\[A_i(t) = \{\alpha(p) | f(p) = j \wedge t_j = t_i\}\]
	\end{definition}

	Notice that with this definition it follows that $A_i(0)$ is the entire domain of $\alpha$ for any $i \in N$.
\end{frame}

\begin{frame}{Sensitivity split}
	\begin{lemma}
		Let $(N, \ell, \alpha)$ a heterogeneous parallel game and tolls $t$ where $t_i \ne t_j$ and $x_i(t), x_j(t) > 0$ for some links $i, j \in N$.
		Then the following hold:
		\begin{enumerate}[(i)]
			\item $\as^{(i, j)}(t) > 0$
			\item $\as^{(i, j)}(t) \in [\alpha(0), \alpha(1)]$
			%\item if $\as^{(i, j)}(t) < \alpha(0)$ (or $\as^{(i, j)}(t) > \alpha(1)$) then $x(t) = (0, 1)$ (or $(1, 0)$)
			\item if $\ell_i(x_i(t)) < \ell_j(x_j(t))$ then
			$\sup A_i(t) \le \as^{(i, j)}(t) \le \inf A_j(t)$
		\end{enumerate}
	\end{lemma}
\end{frame}

@@

\begin{frame}{Sensitivity split | Limits}
	\begin{proof}
		$ $
		\begin{enumerate}[(i)]
			\item For $L = \max\{\ell_i(1) - \ell_j(0), \ell_j(1) - \ell_i(0)\}$ we find
			\begin{flalign*}
				\lim_{|t_i - t_j| \rightarrow +\infty}|\as^{(i, j)}(t)| &= \lim_{|t_i - t_j| \rightarrow +\infty}\frac{|\ell_i(x_i(t)) - \ell_j(x_j(t))|}{|t_i - t_j|}\\
				&\le \lim_{|t_i - t_j| \rightarrow +\infty}\frac{L}{|t_i - t_j|} = 0
			\end{flalign*}
		\end{enumerate}
	\end{proof}
\end{frame}

\begin{frame}{Sensitivity split | Limits}
	\begin{proof}
		$ $
		\begin{enumerate}[(ii)]
			\item ...
		\end{enumerate}
	\end{proof}
\end{frame}

@@

\begin{frame}{Sensitivity split | Upper bound}
	\begin{proof}
		...
	\end{proof}
\end{frame}

@@

\begin{frame}{Heterogeneous Pricing Games}
	Zero money sensitivity creates issues.
	\begin{lemma}
		Let $(N, \ell, \alpha)$ where $\exists \epsilon > 0: \alpha(p) = 0 \; \forall p < \epsilon$.
		Let $i \in N$ be a link for which $\ell_i(0) = \min_{j \in N} \ell_i(0)$.
		Then $B_i(t_{-i})$ is unbounded for all $t_{-i} \in \R_+^{|N| - 1}$.
	\end{lemma}
	\begin{proof}
		$\ell_i(0) = \min_{j \in N} \ell_i(0)$, ensures link $i$ will always have flow

		$i$ can select $t_i > \max t_{-i}$ to make link $i$ the lowest-latency link, populated exclusively by players with $\alpha(p) = 0$

		We fix $t_i^\prime$ and we see that
		\[
			\lim_{t_i \rightarrow +\infty} \Pi_i(t_i, t_{-i}) \ge \lim_{t_i \rightarrow +\infty} x_i^\prime(t_i^\prime, t_{-i})t_i = +\infty
		\]
		making in turn $B_i(t_{-i}) = +\infty$.
	\end{proof}
\end{frame}

\begin{frame}{Pseudo-heterogeneous Pricing Games}
	Consider cases where $\alpha(p) = c$ for some $c \in \R_+$.
	\[
		\sum_{i \in N} (\ell(x_i(t)) + c t_i) \cdot (x_i(t) - x_i) \leq 0
	\]

	\begin{lemma}
		Let $\Gm_1 = (N, \ell^{(1)}, c)$ a heterogeneous pricing game with distribution function $\alpha(p) = c$ for some $c > 0$ and $\Gm_2 = (N, \ell^{(2)}, 1)$ a homogeneous pricing game with latencies $\ell^{(2)} = \frac{\ell^{(1)}}{c}$ for the same $c$.
		Then the two games are equivalent.
	\end{lemma}
	We will call such games \textit{pseudo-heterogeneous}.

	Latency-sensitivity relation is lost for general $\alpha$
\end{frame}

\begin{frame}{Pseudo-heterogeneous Pricing Games}
	\begin{figure}
		\centering
		\begin{tikzpicture}[x=3.4cm, y=3.4cm, every node/.style={font=\small}]
			% Axes
			\draw[->] (0,0) -- (-1.1,0);
			\draw[->] (0,0) -- (2.1,0) node[right] {$t_1 - t_2$};
			\draw[->] (0,0) -- (0,1.1) node[above] {$x_1(t)$};

			% Tick marks
			\draw (-1,0) -- (-1,-0.05) node[below] {$-1$};
			\draw (-1/3,0) -- (-1/3,-0.05) node[left=9,below] {$-\frac13$};
			\draw (-1/4,0) -- (-1/4,-0.05) node[right=3,below] {$-\frac14$};
			\draw (0,0) -- (0,-0.05) node[below] {$t_2$};
			\draw (2/4,0) -- (2/4,-0.05) node[below] {$\frac12$};
			\draw (2/3,0) -- (2/3,-0.05) node[below] {$\frac23$};
			\draw (2,0) -- (2,-0.05) node[below] {$2$};
			\draw (0,1) -- (0.05,1) node[right] {$1$};
			\draw (0,2/3) -- (-0.05,2/3) node[left] {$\frac23$};

			% Flow function graphs
			\draw[thick, blue!33] (-1,1) -- (2,0) node[above, black] {$\alpha = 1$};
			\draw[thick, blue!66] (-1/3,1) -- (2/3,0) node[above right, black] {$\alpha = 3$};
			\draw[thick, blue!100] (-1/4,1) -- (2/4,0) node[black] at (0.2,0.17) {$\alpha = 4$};
		\end{tikzpicture}
		\caption{Flow function for link $1$ of Example for $\alpha(p) = 1, 3, 4$.}
	\end{figure}
\end{frame}

>>>>

\mode<presentation>
{
	\usetheme[subsectionpage=simple,progressbar=foot,numbering=fraction,background=light,block=fill]{metropolis}
	\usecolortheme{default}
	\usefonttheme{default}
	\setbeamercolor{example text}{fg=mDarkTeal}
	\setbeamertemplate{navigation symbols}{}
	\setbeamertemplate{caption}[numbered]
	\setbeamertemplate{frame footer}{Thomas Pappas | ALMA }
}

@@

\title[]{Pricing Games in Heterogeneous Parallel Networks}
\author[Thomas Pappas]{Thomas Pappas}
\institute[ALMA]{
	\begin{columns}
		\column{0.4\textwidth}
		\begin{figure}
			\centering
			\includegraphics[scale=0.1]{alma.png}
		\end{figure}
		\column{0.5\textwidth}
		ALMA \\
		\tiny{INTER-INSTITUTIONAL GRADUATE PROGRAM \\
			"ALGORITHMS, LOGIC AND DISCRETE MATHEMATICS"}
	\end{columns}
}
%\date{\today}
\date{February 10, 2025}

@@

\section{Brief History}

\begin{frame}{\insertsection}
	Selfish routing can model and solve a variety of real-world problems in economics, transportation and more.
	\\[20pt]
	\begin{tikzpicture}[scale=0.9, every node/.style={font=\small,align=center}]
		\draw (0,-0.15) node[below] {Pigou} -- (0,0.15) node[above] {$1920$};
		\draw (0,0) -- (6,0);
		\draw (6,-0.15) node[below] {Beckman\\et al.} -- (6,0.15) node[above] {$1956$};
		\draw (6,0) -- (9,0);
		\draw (9,-0.15) node[below] {Rosenthal} -- (9,0.15) node[above] {$1973$};
		\draw (9,0) -- (10,0);

		\draw (0,-2.65) node[below] {Cole\\et al.} -- (0,-2.35) node[above] {$2003$};
		\draw (0,-2.5) -- (2,-2.5);
		\draw (2,-2.65) node[below] {Acemoglu\\\& Ozdaglar} -- (2,-2.35) node[above] {$2007$};
		\draw (2,-2.5) -- (7.5,-2.5);
		\draw (7.5,-2.65) node[below] {Correa\\et al.} -- (7.5,-2.35) node[above] {$2018$};
		\draw (7.5,-2.5) -- (9,-2.5);
		\draw (9,-2.65) node[below] {Harks\\et al.} -- (9,-2.35) node[above] {$2019$};
		\draw (9,-2.5) -- (10,-2.5);
	\end{tikzpicture}
\end{frame}

\section{Preliminaries}

\subsection{Our model}

\begin{frame}{Preliminaries | Our model}
	\begin{center}
		Heterogeneous Non-atomic $n$-link Parallel Network\\
		Toll Congestion Pricing Game
	\end{center}
\end{frame}
\begin{frame}{Preliminaries | Our model}
	\begin{center}
		\textbf{Heterogeneous} Non-atomic $n$-link Parallel Network\\
		Toll Congestion \textbf{Pricing} Game
	\end{center}
\end{frame}

\begin{frame}{Preliminaries | Our model}
	\;
	\begin{block}{$2$-level game}
		\begin{enumerate}
			\item Shelfish routing game, flow on minimum cost paths
			\item Profit maximisation game for link operators
		\end{enumerate}
	\end{block}
\end{frame}

\begin{frame}{Preliminaries | Selfish routing (1\textsuperscript{st} level)}
	\;
	\begin{block}{Non-atomic $n$-link Parallel Network Game}
		A \textbf{Parallel Network} is a directed graph $G = (\{s, t\}, N)$, where $N = \{1, \dots, n\}$ a set of $n$ parallel $s-t$ links.

@@

\begin{frame}{Preliminaries | Selfish routing (1\textsuperscript{st} level)}
	\;
	\begin{block}{Non-atomic $n$-link Parallel Network Game}
		Flow $f: [0, 1] \rightarrow N$ is a Lebesque measurable function assigning players to links.

@@

\begin{frame}{Preliminaries | Selfish routing (1\textsuperscript{st} level) | Example}
\begin{center}
	\begin{tikzpicture}[scale=1.4, every node/.style={font=\small}]
		% Nodes
		\node[circle, draw, fill=blue!20, minimum size=0.8cm] (s) at (0,0) {$s$};
		\node[circle, draw, fill=blue!20, minimum size=0.8cm] (t) at (4,0) {$t$};

		% Links
		\draw[->, thick] (s) to[bend left=35] node[midway, above] {$2x$} (t);
		\draw[->, thick] (s) to node[midway, above] {$x + 1$} (t);
		\draw[->, thick] (s) to[bend right=35] node[midway, above] {$x + 2$} (t);
	\end{tikzpicture}
\end{center}
Flow $x = \left(\frac23, \frac13, 0\right)$ has all players on minimum latency links.
\end{frame}

\begin{frame}{Preliminaries | Selfish routing (1\textsuperscript{st} level)}
	Tolls $t \in \R_+^{|N|}$ can be assigned to links, affecting player cost.

	In \textbf{homogeneous} networks, player $p$ on link $i$ experiences total cost $c_i(p) = \ell_i(x_i) + t_i$.

	In \textbf{heterogeneous} networks, players value time-money differently, so we add a weight $\alpha$ to the toll (money) cost.

	Player $p$ on link $i$ experiences total cost $c_i(p) = \ell_i(x_i) + \alpha(p) \cdot t_i$.
	\begin{block}{Distribution function $\alpha: [0, 1] \rightarrow [0, +\infty]$}
		\begin{itemize}
			\item players are ordered w.r.t. sensitivity
			\item $\alpha$ is non-decreasing
		\end{itemize}
	\end{block}
\end{frame}

\begin{frame}{Preliminaries | Selfish routing (1\textsuperscript{st} level)}
	In homogeneous networks, all players view link costs the same.
	\begin{definition}
		For a given set of tolls $t$, a flow $x$ is a \textit{Wardrop equilibrium for $t$} if $\forall i, j \in N$ with $x_i > 0$ it holds that
		\begin{equation*}
			\ell_i(x_i) + t_i \leq \ell_j(x_j) + t_j
		\end{equation*}
	\end{definition}
	Links with $x_i > 0$ have $\ell_i(x_i) + t_i = K$ for some $K > 0$.

	Equilibrium is indifferent to uniform variations of tolls ($t^\prime = t + c$).
\end{frame}

\begin{frame}{Preliminaries | Selfish routing (1\textsuperscript{st} level)}
	\begin{lemma}[variational inequality\footcites{beckmann1956studies}{dafermos1973toll}]
		A flow $x$ is a Wardrop equilibrium for $t$ if and only if for all feasible flows $x^\prime$,
		\[\sum_{i \in N} (\ell_i(x_i) + t_i) \cdot (x_i - x_i^\prime) \leq 0\]
	\end{lemma}
\end{frame}

\begin{frame}{Preliminaries | Selfish routing (1\textsuperscript{st} level)}
	\begin{definition}
		For a given set of tolls $t$, a flow $x$ is a \textit{Nash equilibrium for $t$} if $\forall p \in [0, 1]$ and $\forall i \in N$ it holds that
		\begin{equation*}
			c_{f(p)}(p) \leq c_i(p)
		\end{equation*}
	\end{definition}
	N.E. always exists and is unique w.r.t. costs for homogeneous\footcite{beckmann1956studies} and heterogeneous\footcites{1973JSP.....7..295S}{MILCHTAICH1996111} networks.
	We denote it by $x(t)$.
\end{frame}

\begin{frame}{Preliminaries | Selfish routing (1\textsuperscript{st} level) | Example}
\begin{center}
	\begin{tikzpicture}[scale=1.4, every node/.style={font=\small}]
		% Nodes
		\node[circle, draw, fill=blue!20, minimum size=0.8cm] (s) at (0,0) {$s$};
		\node[circle, draw, fill=blue!20, minimum size=0.8cm] (t) at (4,0) {$t$};

		% Links
		\draw[->, thick] (s) to[bend left=35] node[midway, above] {$2x$} (t);
		\draw[->, thick] (s) to node[midway, above] {$x + 1$} (t);
		\draw[->, thick] (s) to[bend right=35] node[midway, above] {$x + 2$} (t);
	\end{tikzpicture}
\end{center}
For homogeneous players and tolls $t = \left(4, 2, 1\right)$ we get
\[x(t) = \left(0, \frac12, \frac12\right)\]
since $\forall p \in [0, 1]$ it holds $c_2(p) = c_3(p) = 7/2$ and $c_1(p) = 4$.
\end{frame}

\begin{frame}{Preliminaries | Pricing competition (2\textsuperscript{nd} level)}
	Links are owned by agents who compete for profit.
	\begin{block}{Profit}
		For given set of tolls $t \in \R_+^{|N|}$, link operator $i$ gains profit
		\[\Pi_i(t) = x_i(t) \cdot t_i\]
	\end{block}
	\begin{block}{Best response}
		For fixed tolls assignments from remaining link operators $t_{-i} = t \setminus \{t_i\}$, link operator $i$ will try and maximise their profit
		\[B_i(t_{-i}) = \argmax_{t_i \ge 0} \Pi(t_i, t_{-i})\]
	\end{block}
\end{frame}

\begin{frame}{Preliminaries | Pricing competition (2\textsuperscript{nd} level)}
	\begin{block}{Nash Equilibrium ($t^*$)}
		A set of tolls $t^*$ is a \textit{Nash Equilibrium for the pricing game} if $\forall i \in N$ and $\forall t_i^\prime \in \R_+$
		\[\Pi_i(t_i^*, t_{-i}^*) \geq \Pi_i(t_i^\prime, t_{-i}^*)\]
	\end{block}
	\begin{block}{Nash Equilibrium ($t^*$)}
		A set of tolls $t^*$ is a \textit{Nash Equilibrium for the pricing game} if
		$\forall i \in N$ we have
		\[t^* = (B_i(t_{-i}^*))_{i \in N}\]
	\end{block}
\end{frame}

\begin{frame}{Preliminaries | Our model}
	We will describe a pricing game as the tuple $\Gm = (N, \ell, \alpha)$ where
	\begin{itemize}
		\item $N = \{1, 2, \cdots, n\}$ the links
		\item $\ell = (\ell_i)_{i \in N}$ the latency functions
		\item $\alpha$ the distribution function
	\end{itemize}
	A homogeneous game can be described as $(N, \ell, 1)$.
\end{frame}

\subsection{Game equivalence}

\begin{frame}{Preliminaries | Game equivalence}
	\begin{definition}[Game equivalence]
		Let $\Gm_1, \Gm_2$ be two $n$-link Network Congestion Games.
		$\Gm_1$ and $\Gm_2$ are called \textbf{equivalent} if and only if for all tolls $t \in \R_+^{|N|}$ it holds that $x^{(1)}(t) = x^{(2)}(t)$, with $x^{(1)}(t), x^{(2)}(t)$ being the Nash Equilibria for $t$ in $\Gm_1, \Gm_2$ respectively.
	\end{definition}
	Equivalency means same tolls cause same flow.

	The two pricing competition games played on two equivalent network congestion games are identical.
\end{frame}

\subsection{Homogeneous networks}

\begin{frame}{Preliminaries | Homogeneous networks}
	\begin{block}{Flow formula\footcite{Harks_2019}}
		Define $N(t) = \{i \in N | x_i(t) > 0\}$.
		For affine latency functions $\ell_i(x) = a_i x + b_i$, $a_i > 0, b_i \ge 0$ and by solving $\ell_i(x_i) + t_i = K$ with $\sum_{i \in N} x_i = 1$, calculate $K$ and get for all $i \in N$
		\begin{equation*}
			x_i(t) = \frac{1 + \sum_{j \in N(t)}\frac{b_j + t_j - b_i - t_i}{a_j}}{\sum_{j \in N(t)}\frac{a_i}{a_j}}
		\end{equation*}
	\end{block}
\end{frame}

\begin{frame}{Preliminaries | Homogeneous networks}
	\begin{block}{Full Wardrop support assumption}
		$x_i(0) > 0$ for all $i \in N$
	\end{block}
	\begin{block}{Pricing N.E. properties\footcite{Harks_2019}}
		$\Pi_i(t)$ is either linear or quadratic, therefore $|B_i(t_{-i})| = 1$.
		If the \textit{full Wardrop support assumption} is satisfied then $t^*$ is unique, $x_i(t^*) > 0$ and $t_i^* > 0$ for all $i \in N$ and
		\begin{equation*}
			t_i^* = \left(a_i + \frac{1}{\sum_{j \ne i} \frac{1}{a_j}}\right) \cdot x_i(t^*)
		\end{equation*}
	\end{block}
\end{frame}

%\begin{frame}{Preliminaries | Homogeneous players | Example}
%	\begin{example}
%	\end{example}
%	$x(0) = \left(\frac23, \frac13\right), \; x(3, 2) = \left(\frac14, \frac34\right)$
%\end{frame}

\subsection{Heterogeneous networks}

\begin{frame}{Preliminaries | Heterogeneous players}
	\begin{lemma}
		For $\Gm = (N, \ell, \alpha)$ with tolls $t$ and flow $x(t)$ the Nash equilibrium for $t$, it holds for all $i, j \in N$ with $x_i(t), x_j(t) > 0$ that
		\begin{enumerate}[(i)]
			\item $\ell_i(x_i(t)) < \ell_j(x_j(t))$ iff $t_i > t_j$
			\item $\ell_i(x_i(t)) = \ell_j(x_j(t))$ iff $t_i = t_j$
			\item $\ell_i(x_i(t)) > \ell_j(x_j(t))$ iff $t_i < t_j$
		\end{enumerate}
	\end{lemma}
	\begin{proof}
		Assume $\ell_i(x_i(t)) < \ell_j(x_j(t))$ and $t_i < t_j$ for some $i, j \in N$.
		Then for \textbf{all} players $c_i(p) < c_j(p)$ so $x_j(t) > 0$ is a contradiction.
	\end{proof}
\end{frame}

\begin{frame}{Preliminaries | Heterogeneous players}
	Latencies are viewed the same for all players.

@@

%\begin{frame}{Preliminaries | Heterogeneous players}
%	\begin{example}
%		Let $([2], \ell, \alpha)$ with $\ell_1(x) = 2x, \ell_2(x) = x + 1$ and $\alpha(p) = p + 1$.
%	\end{example}
%	$x(0) = \left(\frac23, \frac13\right), \; x(3, 2) = \left(\frac14, \frac34\right)$
%\end{frame}

@@

	In example the users are organised around the one for which $c_1(p) = c_2(p)$.

@@

\begin{frame}{Sensitivity split}
	\begin{definition}
		\label{definition:alpha_flow_sets}
		Let $(N, \ell, \alpha)$.
		We define as $A_i(t), A_i: \R_+^n \rightarrow \mathcal{P}(\R_+)$ the set of all possible $\alpha(p)$ values of players $p$ using link $i$ in $x(t)$.
		\[A_i(t) = \{\alpha(p) | f(p) = j \wedge t_j = t_i\}\]
	\end{definition}
\end{frame}

\begin{frame}{Sensitivity split}
	\begin{lemma}
		Let $(N, \ell, \alpha)$ and tolls $t$ where $t_i \ne t_j$ and $x_i(t), x_j(t) > 0$ for some links $i, j \in N$.
		Then:
		\begin{enumerate}[(i)]
			\item $\as^{(i, j)}(t) > 0$
			\item $\as^{(i, j)}(t) \in [\alpha(0), \alpha(1)]$
			%\item if $\as^{(i, j)}(t) < \alpha(0)$ (or $\as^{(i, j)}(t) > \alpha(1)$) then $x(t) = (0, 1)$ (or $(1, 0)$)
			\item if $\ell_i(x_i(t)) < \ell_j(x_j(t))$ then
			$\sup A_i(t) \le \as^{(i, j)}(t) \le \inf A_j(t)$
		\end{enumerate}
	\end{lemma}
\end{frame}

@@

@@

@@

\begin{frame}{Pseudo-heterogeneous Pricing Games}
	Consider distribution functions $\alpha(p) = c$ for some $c > 0$.

	Players again all view link costs the same.
	\[c_i(p) = \ell_i(x_i) + c t_i\]
	Behaviour should be homogeneous with tolls "mapped" to $t \rightarrow t/c$.

	Also note that 
	\[c_i(p) = c \left(\frac1c \ell_i(x_i) + t_i\right)\]
	where $\frac1c \ell_i(x_i) = \frac{a_i}{c} x_i + \frac{b_i}{c}$ affine.
\end{frame}

\begin{frame}{Pseudo-heterogeneous Pricing Games}
	\begin{lemma}
		Let $\Gm_1 = (N, \ell^{(1)}, \alpha)$ where $\forall p \in [0, 1] \; \alpha(p) = c$ for some $c \in \R_+$ and $\Gm_2 = (N, \ell^{(2)}, 1)$ where $\ell^{(2)} = \frac{\ell^{(1)}}{c}$ for the same $c$.
		Then the two games are equivalent.
	\end{lemma}
	\begin{proof}
		For any $t \in \R_+^n$ and any flow $x_i$
		\[
			\sum_{i \in N} \left(\ell_i^{(1)}(x_i^{(2)}(t)) + c t_i\right) \left(x_i^{(2)}(t) - x_i\right) \leq 0
		\]
		$x^{(2)}(t)$ is the unique N.E. for $t$ in $\Gm_1$ so $x^{(1)}(t) = x^{(2)}(t)$.
	\end{proof}
	Costs are proportional.
\end{frame}

\begin{frame}{Pseudo-heterogeneous Pricing Games}
	We will call such games \textit{pseudo-heterogeneous}.

	Uniform increase in money-sensitivity is equivalent to uniform decrease in latencies (lost for general $\alpha$ functions).

	\begin{lemma}
		Let $\Gm_1 = \left(N, \frac{\ell}{c_1}, 1\right), \Gm_2 = \left(N, \frac{\ell}{c_2}, 1\right)$.
		Then $x^{(1)}(c_2 t) = x^{(2)}(c_1 t)$.
	\end{lemma}
	\begin{proof}
		\[
			\begin{aligned}[t]
				&\sum_{i \in N} \left(\frac{1}{c_1}\ell_i(x_i^{(1)}(c_2 t)) + c_2 t_i\right) \left(x_i^{(1)}(c_2 t) - x_i\right) \le 0\\
				\Leftrightarrow &\sum_{i \in N} \left(\frac{1}{c_2}\ell_i(x_i^{(1)}(c_2 t)) + c_1 t_i\right) \left(x_i^{(1)}(c_2 t) - x_i\right) \le 0
			\end{aligned}
		\]
	\end{proof}
\end{frame}

\begin{frame}{Pseudo-heterogeneous Pricing Games}
\begin{lemma}
	Let $\Gm_1 = (N, \ell, c_1)$ and $\Gm_2 = (N, \ell, c_2)$, $c_1, c_2 > 0$.
	Then
	\begin{enumerate}[$(i)$]
		\item $x^{(1)}(c_2 t) = x^{(2)}(c_1 t)$
		\item $\frac{\Pi_i^{(1)}(c_2 t)}{\Pi_i^{(2)}(c_1 t)} = \frac{c_2}{c_1}$
		\item $\frac{B_i^{(1)}(c_2t_{-i})}{B_i^{(2)}(c_1 t_{-i})} = \frac{c_2}{c_1}$
	\end{enumerate}
\end{lemma}
\begin{proof}
	\begin{enumerate}[$(i)$]
		\item Consider $\Gm_3 = (N, \ell/c_1, 1), \Gm_4 = (N, \ell/c_2, 1)$.\\
		Then $x^{(1)}(c_2 t) = x^{(3)}(c_2 t) = x^{(4)}(c_1 t) = x^{(2)}(c_1 t)$.
		\item and $(iii)$ follow from definitions.
		\vspace{-20pt}
	\end{enumerate}
\end{proof}
\end{frame}
